---
title: "PA1_template"
author: "Paula Sichel"
date: "December 16, 2015"
output: html_document
---

##Access the .zip file from the course website, unzip as .csv file##
```{r, echo=TRUE}
temp <- tempfile()
download.file("http://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip", 
              temp)
temp <- unz(temp, "activity.csv")
activity <- read.csv(temp)
unlink(temp)
```

##Create a historgram of the activity dataset##
```{r, echo=TRUE}
activity$date <- as.Date(activity$date)
days <- aggregate(steps ~ date, data=activity, FUN="sum")
hist(days$steps, main="Histogram of activity")
```

###Calculate the median and mean ###
```{r, echo=TRUE}
median(days$steps, na.rm=TRUE)

mean(days$steps, na.rm=TRUE)
```

##Look at the average daily activity pattern##
```{r, echo=TRUE}
pattern <- aggregate(steps ~ interval, data=activity, FUN="sum")
plot(pattern$interval, pattern$steps, type="l", main="Daily activity pattern")
```
  
###Question: Which 5-min interval contains the max number of steps?###
```{r, echo=TRUE}
## this is the value of max steps
max(pattern$steps, na.rm=TRUE)
```
**Using View(pattern), when the number of steps = 10927,**
**the interval is *835*.  This corresponds to 8:35am (I think)** 
  
##Calculate the total number of missing values##
```{r, echo=TRUE}
nrow(subset(activity, is.na(steps)))
```
  
##Input missing values -- fill all N/As with zero##
```{r, echo=TRUE}
steps <- c()
for (i in 1:nrow(activity)) {
  if (is.na(activity$steps[i])) {
    steps[i] = 0
  } else {
    steps[i] <- activity$steps[i]
  }
}
date <- activity$date
interval <- activity$interval
fullset <- data.frame(steps, date, interval)
```
##Here is the Histogram for the new data set (no N/As)##
```{r, echo=TRUE}
fulldays <- aggregate(steps ~ date, data=fullset, FUN="sum")
hist(fulldays$steps, main="Histogram for new data set")
```

##Re-calculate the median and mean of the new data set##
```{r, echo=TRUE}
median(fulldays$steps, na.rm=TRUE)

mean(fulldays$steps, na.rm=TRUE)
```
These values are different (obviously) from the original data set with N/As

##Create plots of weekday and weekend activities##
```{r, echo=TRUE}
fullset$daytype <- sapply(fullset$date, function(d) {
  dow <- weekdays(d)
  if (dow == 'Saturday' || dow == 'Sunday') {
      'weekend'
  } else {
    'weekday'
  }
})
weekdays <- subset(fullset, daytype == 'weekday')
weekday_intervals <- aggregate(steps ~ interval, data=weekdays, FUN="sum")

weekends <- subset(fullset, daytype == 'weekend')
weekend_intervals <- aggregate(steps ~ interval, data=weekends, FUN="sum")

plot(weekday_intervals$interval, weekday_intervals$steps, type="l", main="Weekday activity pattern")

plot(weekend_intervals$interval, weekend_intervals$steps, type="l", main="Weekend activity pattern")


```

###Question: Are there differences in the weekday and weekend patterns?###
Yes. During the weekdays there is a spike of activity around 8:30am.
On the weekends, the activity pattern is dynamic throughout the day.
Overall the person is active during the same range of hours no matter the day.





