---
title: "PA1_template"
author: "Paula Sichel"
date: "December 16, 2015"
output: html_document
---

##Access the zip file from the course website, unzip as .csv file##
```{r, echo=TRUE}
temp <- tempfile()
download.file("http://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip", 
              temp)
temp <- unz(temp, "activity.csv")
activity <- read.csv(temp)
unlink(temp)
```

##Create a historgram of the activity dataset##
```{r, echo=TRUE}
activity$date <- as.Date(activity$date)
days <- aggregate(steps ~ date, data=activity, FUN="sum")
hist(days$steps)
```

###Calculate the median and mean ###
```{r, echo=TRUE}
median(days$steps, na.rm=TRUE)

mean(days$steps, na.rm=TRUE)
```

##Look at the average daily activity pattern##
```{r, echo=TRUE}
pattern <- aggregate(steps ~ interval, data=activity, FUN="sum")
plot(pattern$interval, pattern$steps, type="l")
```
  
###Question: Which 5-min interval contains the max number of steps?###
```{r, echo=TRUE}
## this is the value of max steps
max(pattern$steps, na.rm=TRUE)
```
Using View(pattern), when the number of steps = 10927,
the interval is **835**.  This corresponds to 8:35am (I think)  
  
##Calculate the total number of missing values##
```{r, echo=TRUE}
nrow(subset(activity, is.na(steps)))
```
  
##Input missing values -- fill all N/As with zero##
```{r, echo=TRUE}
steps <- c()
for (i in 1:nrow(activity)) {
  if (is.na(activity$steps[i])) {
    steps[i] = 0
  } else {
    steps[i] <- activity$steps[i]
  }
}
date <- activity$date
interval <- activity$interval
fullset <- data.frame(steps, date, interval)
```
##Here is the Histogram for the new data set (no N/As)##
```{r, echo=TRUE}
fulldays <- aggregate(steps ~ date, data=fullset, FUN="sum")
hist(fulldays$steps)
```

##Re-calculate the median and mean of the new data set##
```{r, echo=TRUE}
median(fulldays$steps, na.rm=TRUE)

mean(fulldays$steps, na.rm=TRUE)
```

##Question: Are there differences weekday vs. weekend activity patterns?##





